Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-19 talk/vmil2012/paper.tex
explain the compact bit representation

@@

Adding this additional information is done as follows.
So far, every variable in the symbolic frames
contains a constant or an SSA variable.
After allocation removal the variables in the symbolic frames can also contain
``virtual'' objects.
These are objects that were not allocated so far,
because the optimizer removed their allocation.
The virtual objects in the symbolic frames describe exactly
how the heap objects that have to be allocated on guard failure look like.
To this end, the content of the every field of the virtual object is described
in the same way that the local variables of symbolic frames are described.
The fields of the virtual objects can therefore be SSA variables, constants
or other virtual objects.

@@

* High level handling of resumedata

- frames consist of a PC and local variables

compression approaches:
- use fact that outer frames don't change in the part of the trace that is in the inner frame
- compact bit-representation for constants/ssa vars

interaction with optimization
- guard coalescing
- virtuals
  - most virtuals not changed between guards

>>>>

In addition to sharing as much as possible between subsequent guards
a compact representation of the local variables of symbolic frames is used.
Every variable in the symbolic frame is encoded using two bytes.
Two bits are used as a tag to denote where the value of the variable
comes from.
The remaining 14 bits are a payload that depends on the tag bits.

The possible source of information are:

\begin{itemize}
    \item For small integer constants
        the payload contains the value of the constant.
    \item For other constants
        the payload contains an index into a per-loop list of constants.
    \item For SSA variables,
        the payload is the number of the variable.
    \item For virtuals,
        the payload is an index into a list of virtuals, see next section.
\end{itemize}

@@

Adding this additional information is done as follows.
So far, every variable in the symbolic frames
contains a constant or an SSA variable.
After allocation removal the variables in the symbolic frames can also contain
``virtual'' objects.
These are objects that were not allocated so far,
because the optimizer removed their allocation.
The virtual objects in the symbolic frames describe exactly
how the heap objects that have to be allocated on guard failure look like.
To this end, the content of the every field of the virtual object is described
in the same way that the local variables of symbolic frames are described.
The fields of the virtual objects can therefore be SSA variables, constants
or other virtual objects.
They are encoded using the same compact two-byte representation
as local variables.

@@
